\documentclass[UTF8, a4paper, 10.5pt, twocolumn, fontset=none]{ctexart}

\usepackage[top=2.0cm, bottom=2.0cm, left=1.8cm, right=1.8cm, columnsep=0.6cm]{geometry}
\setlength{\columnseprule}{0pt}

\usepackage{fontspec}
\usepackage{xeCJK}
\setCJKmainfont[BoldFont={PingFang SC Semibold}, ItalicFont={Kaiti SC}]{Songti SC}
\setCJKsansfont{PingFang SC}
\setCJKmonofont{STSong}
\xeCJKsetup{CJKecglue={\hskip 0.15em plus 0.05em minus 0.05em}}
\usepackage{booktabs}
\usepackage{tikz}
\usetikzlibrary{positioning, arrows.meta, shapes.geometric, fit, backgrounds}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xurl}
\usepackage{caption}
\usepackage{titlesec}
\usepackage[numbers,sort&compress]{gbt7714}

\pagestyle{plain}

\captionsetup{font=small, labelsep=quad}
\titleformat{\section}{\large\bfseries}{\thesection}{0.6em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{0.5em}{}
\titleformat{\subsubsection}{\normalsize\bfseries}{\thesubsubsection}{0.5em}{}

\sloppy

\hypersetup{
  colorlinks=true,
  linkcolor=black,
  citecolor=black,
  urlcolor=blue!60!black,
}

\title{Playwright 测试隐性误修复研究\\
\large \mdseries Research on silent false healing in Playwright test repair}

\author{
  高东彪\\
  \small（软视软件（苏州）有限公司，江苏 苏州 \,215000）\\
  \small Gao Dongbiao\\
  \small (Zoom Video Communications (Suzhou), Inc., Suzhou 215000, China)
}
\date{}

\begin{document}

\twocolumn[
  \begin{@twocolumnfalse}
  \maketitle
  \vspace{-12pt}
  \begin{quote}
  \small
  \noindent\textbf{摘\ 要：}为降低 Playwright 测试中脆弱定位器维护成本，文章研究大语言模型（Large Language Model，LLM）驱动的测试自愈是否产生隐性误修复。以 ReproBreak 数据集 koenig 项目 75 个真实可达失效用例为对象，本文在选择器解析层面对 LLM 修复器进行对抗性诊断，并以 HealReact 的 L1/L3 静态基底作为可复现测量平台。结果表明，目标元素被移除时，\texttt{qwen2.5-coder:7b} 在 78.7\% 的用例中生成指向错误元素的可解析选择器，显式放弃提示未改变逐用例判定；\texttt{gpt-4o} 在同一协议下由 84.0\% 降至 68.0\%，但仍保留高比例误修复。静态基底覆盖 80.6\% 的真实失效目标，但该数字不等同于真实 Playwright 运行时通过率。研究认为，无人值守持续集成自愈需要行为重放验证器。

  \vspace{2pt}
  \noindent\textbf{关键词：}测试自愈；大语言模型；Playwright；React；隐性误修复

  \vspace{2pt}
  \noindent\textbf{中图分类号：}TP311.5\quad\textbf{文献标识码：}A

  \vspace{4pt}
  \noindent\textbf{Abstract：} To reduce the maintenance cost of brittle locators in Playwright tests, this paper studies whether large language model (LLM)-driven test self-healing causes silent false healing. Using 75 real reachable break cases from the koenig project in the ReproBreak dataset, we perform an adversarial selector-resolution-level diagnosis and use the L1/L3 static substrate of HealReact as a reproducible measurement platform. The results show that, when the target element is removed, \texttt{qwen2.5-coder:7b} produces resolver-valid selectors pointing to wrong elements in 78.7\% of cases, and an explicit abstention prompt does not change per-case decisions. Under the same protocol, \texttt{gpt-4o} decreases the rate from 84.0\% to 68.0\%, but still leaves many false heals. The static substrate covers 80.6\% of real break targets, but this number is not a real Playwright runtime pass rate. The study concludes that unattended continuous integration self-healing requires a behavioral replay verifier.

  \vspace{2pt}
  \noindent\textbf{Key words：} self-healing test; large language model; Playwright; React; silent false healing

  \vspace{6pt}
  \end{quote}
  \end{@twocolumnfalse}
]

\begingroup
\renewcommand{\thefootnote}{}
\footnotetext{\footnotesize 作者简介：高东彪（1986—），男，工程师，学士；研究方向：AI 在软件测试中的应用。\\*通信作者：高东彪（1986—），男，工程师，学士；研究方向：AI 在软件测试中的应用。E-mail：gdb\_1986@163.com。}
\endgroup
\setcounter{footnote}{0}

\setcounter{section}{-1}
\input{sections/01_intro}
\input{sections/02_background}
\input{sections/03_l1_substrate}
\input{sections/04_findings}
\input{sections/05_discussion}
\input{sections/07_conclusion}

\bibliography{references}

\end{document}
